Interactive Visualization of Hierarchically Structured Data

### 2016-12-07 treelapse.Rmd
New pdfs for doi sankey on pregnancy data

```{r pretermcstslacto, fig.cap = "Zooming into the Lactobacillaceae family, we notice that the difference between the remaining four CSTs is related to which types of Lactobacillus are most prominent."}
knitr::include_graphics("figure/preterm_csts_lacto.png")
```

```{r pretermpreterm, fig.cap = "Samples with high levels of phyla other than Firmicutes appear to be related to preterm births."}
#oknitr::include_graphics("figure/preterm_preterm.png")
```

>>>>

```{r pretermcstslacto, fig.cap = "Zooming into the Lactobacillaceae family, we notice that the difference between the remaining four CSTs is related to which types of Lactobacillus are most prominent."}
knitr::include_graphics("figure/preterm_csts_lacto.pdf")
```

```{r pretermpreterm, fig.cap = "Samples with high levels of phyla other than Firmicutes appear to be related to preterm births."}
knitr::include_graphics("figure/preterm_preterm.pdf")
```
